# MANOVA'S for cluster solutions

**Manova for clusters based on furthest month (hierarchical and k-means give the same solution)**
This is for all participants who did months
                                           
```{r}
summary.manova(fitmanova, test="Wilks")
```


*Univariate F tests for each DV*

 
```{r}
summary.aov(fitmanova)
```

*Pairwise multivariate tests:* 

                                            
```{r}
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu, subset = bestfit_fur %in% c("head","trunk") ))
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu, subset = bestfit_fur %in% c("head","room") ))
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu, subset = bestfit_fur %in% c("room","trunk") ))
```



**Manova for mixed (some participants reg line angles, some furthest)**

This is for all participants who did months. sa20,co3,co4,co9,sa21,sa24 analyzed with furthest month, the rest with reg line angles
                                           
```{r}
summary.manova(fitmanova_mixed, test="Wilks")
```


*Univariate F tests for each DV*

 
```{r}
summary.aov(fitmanova_mixed)
```

*Pairwise multivariate tests:* 

                                            
```{r}
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu, subset = bestfit_month %in% c("head","trunk") ))
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu, subset = bestfit_month %in% c("head","room") ))
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu, subset = bestfit_month %in% c("room","trunk") ))
```


**Manova for clusters based on furthest month (hierarchical and k-means give the same solution)**
This is for 10/10 participants 
                                           
```{r}
summary.manova(fitmanova_fur_both, test="Wilks")
```


*Univariate F tests for each DV*

 
```{r}
summary.aov(fitmanova_fur_both)
```

*Pairwise multivariate tests:* 

                                            
```{r}
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu_both, subset = bestfit_fur %in% c("head","trunk") ))
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu_both, subset = bestfit_fur %in% c("head","room") ))
summary(manova(cbind(trunk_fit_fur,head_fit_fur,room_fit_fur) ~ bestfit_fur, data=fitClu_both, subset = bestfit_fur %in% c("room","trunk") ))
```


**Manova for mixed (some participants reg line angles, some furthest)**

This is for 10/10
                                           
```{r}
summary.manova(fitmanova_mixed_both, test="Wilks")
```


*Univariate F tests for each DV*

 
```{r}
summary.aov(fitmanova_mixed_both)
```

*Pairwise multivariate tests:* 

                                            
```{r}
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu_both, subset = bestfit_month %in% c("head","trunk") ))
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu_both, subset = bestfit_month %in% c("head","room") ))
summary(manova(cbind(trunk_fit_mixed,head_fit_mixed,room_fit_mixed) ~ bestfit_month, data=fitClu_both, subset = bestfit_month %in% c("room","trunk") ))
```
